Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/experiments.tex
minor change to circuit-region-usage stuff
Minor edit

Our second experiment is a port of the \emph{fluidanimate} benchmark
from the PARSEC suite\cite{bienia11benchmarking}, which does a
particle-based simulation of an incompressible fluid.  Each particle
interacts only with other nearby particles. The benchmark divides the
space in which the fluid can move into a three-dimensional array of
cells such that the range of interaction is limited to just the cells
adjacent (including diagonals) to the one a particle resides in.  The
application divides the array into {\em grids} and assigns each grid to
a thread.  Per-cell locking safely accesses particles in
cells that lie on the edge of a grid.  This fine-grained locking
scheme along with the assumption of a shared address space gives
good scaling in a multi-core processor, but rules out any attempt to run
beyond a single node.

>>>>

Our second experiment is a port of the \emph{fluidanimate} benchmark
from the PARSEC benchmark suite\cite{bienia11benchmarking}, which does a
particle-based simulation of an incompressible fluid.  Each particle
interacts only with other nearby particles. The benchmark divides the
space in which the fluid can move into a three-dimensional array of
cells such that the range of interaction is limited to just the cells
adjacent (including diagonals) to the one a particle resides in.  The
application divides the array into {\em grids} and assigns each grid to
a thread.  Per-cell locking safely accesses particles in
cells that lie on the edge of a grid.  This fine-grained locking
scheme along with the assumption of a shared address space gives
good scaling in a multi-core processor, but rules out any attempt to run
beyond a single node.
